snpArcher: FASTQ -> VCF workflow for WGS data

### 2022-10-27 fastq2vcf_june2022_update.Rmd
Fixed references in RADseq, updated fastq2vcf to most recent version from SW
changing back to original .Rmd files, will make sure it's ok before I go ahead with doing this

---
title: 'snpArcher: FASTQ -> VCF workflow for WGS data'
author: "Sara JS Wuitchik"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: "snpArcher: FASTQ -> VCF workflow for WGS data"
author: "Sara JS Wuitchik"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
```
